|

### 2025-05-06 doc/paper.qmd
Final paper refine-tuning

fig_caption: yes
fontsize: 12pt
ident: yes
always_allow_html: yes
number-sections: true
header-includes:
  - \usepackage[nolists]{endfloat}
  - \usepackage{setspace}\onehalfspacing
  - \setlength{\parindent}{4em}
  - \setlength{\parskip}{0em}
  - \usepackage[hang,flushmargin]{footmisc}
  - \usepackage{caption}
  - \captionsetup[table]{skip=24pt,font=bf}
  - \usepackage{array}
  - \usepackage{threeparttable}
  - \usepackage{adjustbox}
  - \usepackage{graphicx}
  - \usepackage{csquotes}
  - \usepackage{indentfirst}
  - \usepackage[margin=1in]{geometry}
  - \usepackage{ragged2e} #for declaration intend
---

>>>>

fig_caption: yes
fontsize: 12pt # 12-point font acc. to Accounting guidelines
ident: yes
always_allow_html: yes
number-sections: true
header-includes:
  - \usepackage[nolists]{endfloat}
  - \usepackage{setspace}\onehalfspacing # 1.5 line spacing acc. to Accounting guidelines
  - \setlength{\parindent}{4em}
  - \setlength{\parskip}{0em}
  - \usepackage[hang,flushmargin]{footmisc}
  - \usepackage{caption}
  - \captionsetup[table]{skip=24pt,font=bf}
  - \usepackage{array}
  - \usepackage{threeparttable}
  - \usepackage{adjustbox}
  - \usepackage{graphicx}
  - \usepackage{csquotes}
  - \usepackage{indentfirst}
  - \usepackage[margin=1in]{geometry}
  - \usepackage{ragged2e} #for declaration intend
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
  - \fancyhf{}  % clear headers/footers
  - \renewcommand{\headrulewidth}{0pt}
  - \renewcommand{\footrulewidth}{0pt}
  - \fancyfoot[R]{\makebox[0pt][r]{\thepage\hspace{1in}}} % right-aligned footer # page numbering on lower right margin acc. to WiWi guidelines
  - \setlength{\footskip}{0cm} # acc. to Wiwi guidelines - control a 1 to 1.5 cm gap below page numbers
---
